---
title: Useful R Notes
date: "2020-01-05"
slug: r_notes
---

[Advanced R 2nd edition](https://adv-r.hadley.nz/)

```{r,include=F}
knitr::opts_chunk$set(comment='#>',error=T,message = F,warning = F,fig.align='center',out.width ='90%')
```

这个文章记录我对R的一些练习重点


R 中的所有标准运算符都是函数！包括`+`、`$`、`[`、`(`



```{r}
for (i in 1:2) print(i)
`for`(i, 1:2, print(i))

{ print(1); print(2); print(3) }
`{`(print(1), print(2), print(3))
```

2020年1月7日阅读[Advanced R](http://adv-r.had.co.nz/Introduction.html) 关于函数的章节。

`do.call`可以进行函数求值：

```{r}
do.call(mean, list(1:10, na.rm = TRUE))
mean(1:10, na.rm = TRUE)
```

R 函数默认惰性求值

Infix functions 中缀函数

### Install R on Ubuntu 18.04

```
sudo apt-key adv --keyserver keyserver.ubuntu.com --recv-keys E298A3A825C0D65DFD57CBB651716619E084DAB9

sudo add-apt-repository 'deb https://cloud.r-project.org/bin/linux/ubuntu bionic-cran35/'

sudo apt update

sudo apt install r-base
```

# R Environment

The job of an environment is to associate, or bind, a set of names to a set of values. You can think of an environment as a bag of names, with no implied order (i.e. it doesn’t make sense to ask which is the first element in an environment)

R environments always have parents.

The global environment `global_env()` is sometimes called your “workspace”, as it’s where all interactive (i.e. outside of a function) computation takes place

Each package attached by `library()` or `require()` becomes one of the parents of the global environment.



stop("This is what an error looks like")









