---
title: Useful R Notes
date: "2020-01-05"
slug: r_notes
html_document:
    toc: true
    highlight: tango
---

[Advanced R 2nd edition](https://adv-r.hadley.nz/)

```{r,include=F}
knitr::opts_chunk$set(comment='#>',error=T,message = F,warning = F,fig.align='center',out.width ='90%',collapse = T)
```

这个文章记录我对R的一些练习重点


R 中的所有标准运算符都是函数！包括`+`、`$`、`[`、`(`




```{r}
for (i in 1:2) print(i)
`for`(i, 1:2, print(i))

{ print(1); print(2); print(3) }
`{`(print(1), print(2), print(3))
```

2020年1月7日阅读[Advanced R](http://adv-r.had.co.nz/Introduction.html) 关于函数的章节。

`do.call`可以进行函数求值：

```{r}
do.call(mean, list(1:10, na.rm = TRUE))
mean(1:10, na.rm = TRUE)
```

R 函数默认惰性求值

Infix functions 中缀函数

### Install R on Ubuntu 18.04

```
sudo apt-key adv --keyserver keyserver.ubuntu.com --recv-keys E298A3A825C0D65DFD57CBB651716619E084DAB9

sudo add-apt-repository 'deb https://cloud.r-project.org/bin/linux/ubuntu bionic-cran35/'

sudo apt update

sudo apt install r-base
```

# R Environment

The job of an environment is to associate, or bind, a set of names to a set of values. You can think of an environment as a bag of names, with no implied order (i.e. it doesn’t make sense to ask which is the first element in an environment)

R environments always have parents.

The global environment `global_env()` is sometimes called your “workspace”, as it’s where all interactive (i.e. outside of a function) computation takes place

Each package attached by `library()` or `require()` becomes one of the parents of the global environment.



stop("This is what an error looks like")


If you use a vector with `[[`, it will subset recursively, i.e. `x[[c(1, 2)]]` is equivalent to `x[[1]][[2]]`. This is a quirky feature that few know about, so I recommend avoiding it in favour of `purrr::pluck()`, which you’ll learn about in Section 4.3.3.

# 

`switch` could be use as `if`:

```{r}
x_option <- function(x) {
  if (x == "a") {
    "option 1"
  } else if (x == "b") {
    "option 2" 
  } else if (x == "c") {
    "option 3"
  } else {
    stop("Invalid `x` value")
  }
}

(switch("c", a = 1, b = 2))
#> NULL
legs <- function(x) {
  switch(x,
    cow = ,
    horse = ,
    dog = 4,
    human = ,
    chicken = 2,
    plant = 0,
    stop("Unknown input")
  )
}
legs("cow")
#> [1] 4
legs("dog")
#> [1] 4

```

for 循环的3个陷阱：

+ 提前设定循环结果存储的对象，使用`vector`函数

```{r}
means <- c(1, 50, 20)
out <- vector("list", length(means))
for (i in 1:length(means)) {
  out[[i]] <- rnorm(10, means[[i]])
}
```

+ 循环长度为0 的变量时可能一步所获，因此改用`seq_along`:

```{r}
means <- c()
out <- vector("list", length(means))
for (i in seq_along(means)) {
  out[[i]] <- rnorm(10, means[[i]])
}
out
```

+ 当遇到S3向量时，for循环会剥离一些属性，此时还是需要使用`seq_along`：

```{r}
xs <- as.Date(c("2020-01-01", "2010-01-01"))
seq_along(xs)
for (i in seq_along(xs)) {
  print(xs[[i]])
}
```

# 数据框索引

```{r}
df <- data.frame(x = 1:3, y = 3:1, z = letters[1:3])

str(df["x"])

str(df[, "x"])
```


```{r}
library(magrittr)
iris %>% head(10)
```

